Linear Variation and an Optimization of Algorithms for Connected Components Labeling in a Binary Image

### 2016-04-20 paper/paper.tex
Fix the obvious typo

The speedup plots on \Cref{fig:normed:DFS,fig:normed:SUF,fig:normed:SUF2}
suggest that the ``2x2 copy'' optimization speeds up the considered methods by
factor greater than 1 for all tested densities. On the other hand, the
``2x2 view'' optimization is showed to be not time-efficient at all for some
densities, slowing down DFS and SUF2 if run on images with densities less than
38\% and 28\% respectively. Utilizing the latter optimization also does not
speed up SUF on images on density approaching 20\%, although it does not slow
down the algorithms either.

>>>>

The speedup plots on \Cref{fig:normed:DFS,fig:normed:SUF,fig:normed:SUF2}
suggest that the ``2x2 copy'' optimization speeds up the considered methods by
factor greater than 1 for all tested densities. On the other hand, the
``2x2 view'' optimization is showed to be not time-efficient at all for some
densities, slowing down DFS and SUF2 if run on images with densities less than
35\% and 25\% respectively. Utilizing the latter optimization also does not
speed up SUF on images on density approaching 20\%, although it does not slow
down the algorithms either.
